Against Spurious Understanding: Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}

### 2024-02-06 body_econdat.tex
last update econdat

Our goal in this section is to not only predict economic growth from the yield curve but also extract meaningful features for downstream inference tasks. In particular, we will now use a neural network architecture.

@@

So far, we considered simple linear data transformations. One might argue that this does not really involve latent embeddings in the way they are typically thought of in the context of deep learning. In Appendix~\ref{appendix:autoencoder}, we present an additional experiment in which we more explicitly seek neural network-based representations that will be useful for downstream tasks. Here, we continue with an example in which LLMs may be used for Economic Sentiment Prediction.

>>>>

So far, we considered simple linear data transformations. One might argue that this does not really involve latent embeddings in the way they are typically thought of in the context of deep learning. Our goal in this section is to not only predict economic growth from the yield curve but also extract meaningful features for downstream inference tasks. In particular, we will now use a neural network architecture.

@@

Next, we continue with an example in which LLMs may be used for Economic Sentiment Prediction.
